Austrian Parliament: MPs transparency and conflict of interest report

### 2021-02-19 _post/2020-07-21-attransperency/attransperency.Rmd
without css

---
title: "Austrian Parliament: MPs transparency and conflict of interest report"
description: |
  Analysis of MP's transparency and conflict of interest report.
date: 07-21-2020

author:
  - first_name: "Roland"
    last_name: "Schmidt"
    url: https://werk.statt.codes
    orcid_id: 0000-0002-6897-1693

@@

creative_commons: CC BY-NC-SA
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = T,
                      dev = "png")
```

@@

```{r echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(extrafont)
loadfonts(device = "win", quiet = T)
library(hrbrthemes)
# hrbrthemes::update_geom_font_defaults(family = "Roboto Condensed",
                                      # size=3)
library(scales)
library(knitr)
library(paletteer)
library(ggtext)
library(glue)
library(gt)
library(DT)
library(pdftools)
library(lemon)
library(ggiraph)

@@

# theme_post <- function() {
  hrbrthemes::theme_ipsum_rc() +
    theme(
      plot.background = element_rect(fill = plot_bg_color, color=NA),
      panel.background = element_rect(fill = plot_bg_color, color=NA),
      plot.margin = margin(l = 0, unit = "cm"),
      plot.title = element_text(
        color = "grey20",
        face = "bold",
        margin = margin(l = 0, unit = "cm"),
        size = 13
      ),
      plot.title.position = "plot",
      plot.subtitle = element_text(
        color = "grey50",
        margin = margin(t = 0.2, b = 0.3, unit = "cm"),
        size = 11
      ),
      plot.caption = element_text(
        color = "grey50",
        size = 8,
        hjust = c(0)
      ),
      plot.caption.position = "panel",
      axis.title.x = element_text(angle = 0,
                                         color="grey50",
                                         hjust=1),
      axis.text.x = element_text(size = 9, 
                                 color = "grey50"),
      axis.title.y = element_blank(),
      axis.text.y = element_text(size = 9,
                                 color="grey50"),
      panel.grid.minor.x = element_blank(),
      panel.grid.major.x = element_blank(),
      panel.grid.minor.y = element_blank(),
      panel.spacing = unit(0.25, "cm"),
      panel.spacing.y = unit(0.25, "cm"),
      strip.text = element_text(
        angle = 0,
        size = 9,
        vjust = 1,
        face = "bold"
      ),
      legend.title = element_text(
        color = "grey30",
        face = "bold",
        vjust = 1,
        size = 7
      ),
      legend.text = element_text(
        size = 7,
        color = "grey30"
      ),
      legend.justification = "left",
      legend.box = "horizontal", # arrangement of multiple legends
      legend.direction = "vertical",
      legend.margin = margin(l = 0, t = 0, unit = "cm"),
      legend.spacing.y = unit(0.07, units = "cm"),
      legend.text.align = 0,
      legend.box.just = "top",
      legend.key.height = unit(0.2, "line"),
      legend.key.width = unit(0.5, "line"),
      text = element_text(size = 5)
    )
#}

theme_post <- function() {
  hrbrthemes::theme_ipsum_rc() 
}

@@

![](austrian-parliament-mps-transparency-and-conflict-of-interest-report_files/list_example - Copy.PNG){width="100%"}

@@

<details open>

<summary>Code: Extract text from pdfs </summary>

```{r}
my_path <- here::here("_blog_data", "MP_activities", "BezBegrBVGPar9-NR.pdf")

@@

```{r echo=FALSE, tidy=FALSE, R.options=list(width=10)}
stringr::str_wrap(df_all$text_raw[1], 10)
```

@@

<details open>

<summary>Code: Extract MPs' names and income category </summary>

```{r}
df_all <- df_all %>%
  mutate(name = str_extract(text_raw, regex("(?<=Einkommenskategorie)(?s).*(?=für das Jahr)", ignore_case = T)) %>%
    str_remove(., "\\(i\\)") %>%
    str_trim()) %>%
  mutate(income_category_19_raw = str_extract(text_raw, regex("(?<=2019:\\s?)\\S"))) %>% 
  mutate(income_category_19=case_when(income_category_19_raw=="-" ~ 0,
                                      TRUE ~ as.numeric(income_category_19_raw))) %>% 
    replace_na(., list(income_category_19="missing")) %>%
  select(-income_category_19_raw)

@@

<details open>

<summary>Code: Account for multi-page declarations </summary>

```{r}
df_income <- df_all %>%
  select(name, income_category_19) %>%
  distinct()
```

```{r}
nrow(df_all)
nrow(df_income)
```

@@

<summary>Code: Number of MPs per income bracket </summary>

```{r}
tbl_income <- df_income %>% 
  count(income_category_19) %>% 
  gt() %>% 
  gt::cols_label(income_category_19=md("**income category**"),
                 n=md("**number of MPs**")) 
```

```{r echo=FALSE}
tbl_income
```

@@

<summary>Code: MPs with with missing income data</summary>

```{r}
df_income_missing <- df_income %>% 
  filter(income_category_19=="missing") %>% 
  mutate(family_name=str_remove(name, ",.*$") %>% 
           str_extract(., "\\S*$"))

@@

```{r echo=FALSE}
tbl_missing
```

@@

<summary>Code: Get entry dates for MPs with missing income data</summary>

@@

#apply funciton to all links
# df_mp_dates <- df %>% 
#   mutate(mp_dates=map(link, ~fn_get_dates(.)))

@@

df_mp_dates <- readr::read_rds(file=here::here("_blog_data", "MP_activities", "MP_dates.rds"))

```{r}
#extract family name for subsequent merger with income data
df_mp_dates <- df_mp_dates %>% 
  mutate(family_name=str_trim(title) %>% 
           str_extract(., regex("^\\S*")))

@@

```{r echo=FALSE}
df_income_missing %>% 
  gt() %>% 
  gt::cols_label(mp_dates=md("**entry date**"),
                 name=md("**MP**"))
```

@@

<summary>Code: Remove MPs joining outside of reporting period </summary>

```{r echo=TRUE}
nrow(df_income)
df_income <- df_income %>% 
  filter(!name %in% df_income_missing$name)
nrow(df_income)
```

@@

<details open>

<summary>Code: Get MPs' gender</summary>

```{r}
#get a clean name, without any academic or prefessional titles
df_income <- df_income %>% 
  mutate(name_family=str_remove(name, ",.*$") %>% 
           str_extract(., "\\S*$"),
         .after=name) %>% 
  mutate(name_clean=name %>% str_remove(., regex(",.*$")) %>% 
           str_remove_all(., regex("\\S*\\.")) %>% 
           str_remove_all(., regex("\\(.*\\)")) %>% 
           str_trim())

@@

<summary>Code: Calculate gender ratios and create plots</summary>

```{r}
df_gender <- df_income %>% 
  group_by(income_category_19, gender) %>% 
  summarise(n_obs=n()) %>% 
  mutate(n_rel_category=n_obs/sum(n_obs)) %>% 
  group_by(gender) %>% 
  mutate(n_gender=sum(n_obs)) %>% 
  ungroup() %>% 
  mutate(n_rel_gender=n_obs/n_gender)

@@

```{r}
pl_gender_category <- df_gender %>% 
  # filter(gender=="female") %>% 
  mutate(gender=fct_rev(gender)) %>% 
  ggplot()+
  labs(title=glue("Austrian Nationalrat: Share of <span style  = color:{gender_colors['female']}>female</span> and <span style = color:{gender_colors['male']}>male</span> MPs per income category"),
       subtitle=str_wrap("Income: average monthly income from professional positions in addition to MPs' salary. Absolute number of female MPs in brackets. Only lower chamber. Data for 2019.", 105),
       y="[income category] average monthly income",
       caption=my_caption)+
  geom_bar(aes(y=income_category_19,
               x=n_obs,
               fill=gender),
           stat="identity",
           position="fill")+
  geom_text(data=. %>% filter(gender=="female"),
            aes(y=income_category_19,
                x=n_rel_category-0.01,
                label=paste0(round(n_rel_category,2) %>% 
                  percent(scale=100),
                  "\n(",
                  n_obs,
                  ")")),
            color="white",
            lineheight=0.6,
            hjust=1,
            stat="identity")+
  geom_vline(xintercept = .5,
             color="white",
             linetype="dashed"
             )+
  scale_fill_manual(values=gender_colors)+
  scale_x_continuous(label=scales::label_percent(),
                     expand=expansion(mult=c(0, 0.05)))+
  scale_y_discrete(labels=income_categories_short,
                   expand=expansion(mult=c(0, 0)),
                   position = "left")+
  theme_post()#+
  # theme(legend.position="none",
  #       plot.title=element_markdown(),
  #       axis.title.x=element_blank(),
  #       axis.title.y.left = element_text(angle = 90,
  #                                        color="grey50",
  #                                        hjust=1),
  #       axis.text.y.left = element_text(),
  #       axis.text.y.right = element_blank(),
  #       axis.title.y.right = element_blank(),
  #       panel.grid.major.y  = element_blank())

pl_gender_category

```{r echo=FALSE, fig.height=6, fig.width=10, include=T, device="ragg_png"}
pl_gender_category

@@

```{r}
pl_gender_intra_dist <- df_gender %>% 
  ggplot()+
  labs(title="Austrian Nationalrat: Distribution of MPs over income groups per gender",
       subtitle=str_wrap("Income: average monthly income from professional positions in addition to MPs' salary. Absolute number of MPs in brackets. Only lower chamber. Data for 2019.", 105),
       x="[income category] average monthly income",
       caption=my_caption)+
  geom_bar(aes(x=income_category_19,
               y=n_rel_gender,
               fill=gender),
           stat="identity")+
  geom_text(aes(x=income_category_19,
                y=n_rel_gender+0.02,
                label=paste0(percent(n_rel_gender, accuracy = 0.1),
                             "\n",
                             "(", n_obs, ")")),
            lineheight=0.7,
            stat="identity")+
  scale_fill_manual(values=gender_colors, 
                    na.value = "grey30")+
  scale_x_discrete(labels=income_categories_short)+
  scale_y_continuous(label=scales::label_percent(accuracy=1),
                     expand=expansion(mult=c(0, 0.1)))+
  facet_wrap(vars(gender))+
  # theme_post()+
  theme(legend.position = "none",
        axis.title.x = element_text(angle = 0,
                                         color="grey50",
                                         hjust=1),)
```

@@

```{r echo=FALSE}
pl_gender_intra_dist
```

# Party affiliation

```{r}
mtcars %>% 
  ggplot()+
  geom_point(aes(
    x=mpg,
    y=disp
  ))
```

## Get MPs' party membership

@@

<summary>Code: Get party affiliation </summary>

```{r}
wiki_link <- "https://de.wikipedia.org/wiki/Liste_der_Abgeordneten_zum_%C3%96sterreichischen_Nationalrat_(XXVII._Gesetzgebungsperiode)"

@@

```{r echo=FALSE}
datatable(df_income %>% select(name, party, gender, income_category_19),
          colnames=c("MP name"="name", "income category"="income_category_19"),
          filter="top",
          options=list(pageLength=10,
                       columnDefs = list(list(className = 'dt-center', targets = 1:3,
                                         searchable=TRUE))),
          rownames = FALSE)
```

@@

<summary>Code: plots on income categories</summary>

```{r}
df_agg <- df_income %>% 
  ungroup() %>%
  mutate(income_category_19_fac=as_factor(income_category_19) %>% 
           fct_inseq()) %>% 
  mutate(party=fct_infreq(party)) %>% 
  group_by(income_category_19, party, .drop = F) %>% 
  summarise(n_obs=n()) %>% 
  group_by(party) %>% 
  mutate(n_obs_total=sum(n_obs)) %>% 
  mutate(n_obs_rel=n_obs/n_obs_total)

pl_rel <- df_agg %>% 
  ggplot()+
  labs(title="Austrian Nationalrat: Relative number of MPs per income category and party",
    subtitle=str_wrap("Percentages are shares of each party's total number of members. Absolute numbers in brackets. Lower chamber only (Nationalrat). Data for 2019.", 105),
    x="[income category] average monthly income",
    caption=my_caption)+
  geom_label(data=. %>% filter(n_obs_rel >0),
            aes(x=party,
                y=n_obs_rel+.3,
                family="Roboto Condensed",
                group=party,
                label=paste0(scales::percent(n_obs_rel,
                                      accuracy=0.1),
                            "\n",
                            "(", n_obs, ")")
                ),
            fill="white",
            label.size=0,
            label.padding = unit(0.1, "lines"),
            lineheight=0.7,
            family="Roboto Condensed",
            position=position_dodge2(width = 1))+
    geom_bar(aes(x=party,
               y=n_obs_rel,
               group=income_category_19,
               fill=party),
           position=position_dodge2(),
           stat="identity"
           )+
  scale_fill_manual(values=party_colors)+
  scale_x_discrete(labels=abbreviate)+
  scale_y_continuous(label=scales::label_percent(),
                     # limits = c(0, 1.15),
                     expand=expansion(mult=c(0, 0.15)))+
  lemon::facet_rep_wrap(vars(income_category_19),                        labeller=labeller(income_category_19=map_chr(income_categories_short, ~str_remove_all(., regex("\\]|\\["))) %>% 
                                                                                             map_chr(., ~str_replace(., regex("\\\n"), ": ")) %>%
                                                                                             map_chr(., ~paste0("Income category ", .))),
                        ncol=2,
                        repeat.tick.labels = TRUE)+
  theme_post()+
  theme(legend.position="none",
        axis.title.x = element_blank())
```

```{r echo=FALSE}
pl_rel
```

@@

```{r echo=FALSE}
pdf_file <- pdftools::pdf_data(pdf = my_path) 
datatable(pdf_file[[8]],
          options=list(pageLength=10,
                       columnDefs = list(list(className = 'dt-center', targets = 0:4)),
                       list(className='dt_left', targets=5)),
          rownames=FALSE)
```

@@

<details open>

<summary>Code: identifying new positions</summary>

```{r}
df_linebreaks <- pdf_file[[8]] %>%
  select(y, text) %>% 
    arrange(y) %>%
    mutate(line_diff = y - dplyr::lag(y, default = 0)) %>%
    mutate(row_jump = case_when(
      line_diff > 11 ~ 1,
      TRUE ~ 0
    )) %>%
    mutate(row_indicator = cumsum(row_jump)) 
```

```{r echo=FALSE}
datatable(df_linebreaks,
          options=list(pageLength=10,
                       columnDefs = list(list(className = 'dt-center', targets = "all"))),
          rownames=FALSE)
```

@@

<details open>

<summary>Code: Table with one row per position</summary>

```{r paged.print=TRUE}
df_rows <- df_linebreaks %>% 
  group_by(row_indicator) %>%
    summarise(text_combined = paste(text, collapse = " ")) %>%
    mutate(text_combined = text_combined %>% str_trim() %>% str_squish())
```

```{r}
df_rows
```

@@

<summary>Code: row numbers of sub-headings</summary>

```{r}
# headings
heading_executive <- df_rows %>%
    filter(str_detect(text_combined, regex("Leitende Stellung in", ignore_case = T))) %>%
    pull(row_indicator)

@@

<details open>

<summary>Code: Function to extract positions </summary>

```{r}
fn_get_positions <- function(x) {
  d <- x %>%
    arrange(y) %>%
    mutate(line_diff = y - dplyr::lag(y, default = 0)) %>%
    mutate(row_jump = case_when(
      line_diff > 11 ~ 1,
      TRUE ~ 0
    )) %>%
    mutate(row_indicator = cumsum(row_jump)) %>%
    group_by(row_indicator) %>%
    summarise(text_combined = paste(text, collapse = " ")) %>%
    mutate(text_combined = text_combined %>% str_trim() %>% str_squish())

@@

<details open>

<summary>Code: Apply function </summary>

```{r}
df_data <- pdf_file %>%
  map_dfr(., fn_get_positions)

@@

```{r echo=FALSE}
datatable(df_count,
          colnames=c("MP name"="name",
                     "# executive pos (total)"="executive_n",
                     "# executive pos not remunerated"="executive_non_remunerated_n",
                     "# other pos"="other_n",
                     "# honorary pos"="honorary_n",
                     "total # pos" = "total_n"),
          options=list(pageLength=10,
                       columnDefs = list(list(className = 'dt-center', targets = "all"))),
          rownames=FALSE)
```

@@

<summary>Code: Number of paid positions and income category</summary>

```{r}
df_income_positions <- df_count2 %>% 
  left_join(., df_income %>% select(gender, income_category_19, name),
            by="name") %>% 
  select(name_clean, name, contains("executive"), contains("other"), party, income_category_19) %>% 
  mutate(positions_paid=(executive_n-executive_non_remunerated_n)+other_n)

@@

```{r echo=FALSE, fig.height=15}
girafe(ggobj = pl_income_positions)

@@

<summary>Code: MPs with no income but paid positions</summary>

```{r}
df_mp5 <- df_income_positions %>% 
  filter(income_category_19==0) %>% 
  filter(positions_paid>0) %>% 
  select(contains("name"), party, executive_n, positions_paid) %>% 
  left_join(., df_positions %>% select(name, executive_positions, other_positions), by=c("name"="name")) %>% 
  pivot_longer(cols=c(contains("positions"), -positions_paid),
               names_to="positions",
               values_to="positions_name") %>% 
  mutate(positions_chr=map(positions_name, deframe) %>% 
           map_chr(., ~paste(., collapse=";\n "))) %>% 
  select(-positions_name) %>% 
  pivot_wider(id_cols=c(name, party),
              names_from=positions,
              values_from=positions_chr)

@@

<details open>

<summary>Code: MP share w at least one add. position</summary>

```{r}
df_bar_position <- df_position_long %>% 
  filter(!position %in% c("executive_non_remunerated_n",
                        "total_n")) %>% 
  group_by(party, position) %>% 
  summarize(n_zero=length(number[number==0]),
            n_non_zero=length(number[number!=0])) %>% 
  ungroup() %>% 
  mutate(perc=n_non_zero/(n_non_zero+n_zero)) %>% 
  mutate(position=fct_relevel(position, "honorary_n", after = 2))

@@

<details open>

<summary>Code: different types of executive positions</summary>

>>>>

---
title: "Austrian Parliament: MPs transparency and conflict of interest report"
description: |
  A short description of the post.

date: 07-21-2020
author:
  - first_name: "Roland"
    last_name: "Schmidt"
    url: https://werk.statt.codes
    orcid_id: 0000-0002-6897-1693

@@

creative_commons: CC BY-NC-SA

---

@@

```{r echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(extrafont)
loadfonts(device = "win", quiet = T)
library(hrbrthemes)
hrbrthemes::update_geom_font_defaults(family = "Roboto Condensed",
                                      size=3)
library(scales)
library(knitr)
library(paletteer)
library(ggtext)
library(glue)
library(gt)
library(DT)
library(pdftools)
library(lemon)
library(ggiraph)

@@

theme_post <- function() {
  hrbrthemes::theme_ipsum_rc() +
    theme(
      plot.background = element_rect(fill = plot_bg_color, color=NA),
      panel.background = element_rect(fill = plot_bg_color, color=NA),
      plot.margin = margin(l = 0, unit = "cm"),
      plot.title = element_text(
        color = "grey20",
        face = "bold",
        margin = margin(l = 0, unit = "cm"),
        size = 13
      ),
      plot.title.position = "plot",
      plot.subtitle = element_text(
        color = "grey50",
        margin = margin(t = 0.2, b = 0.3, unit = "cm"),
        size = 11
      ),
      plot.caption = element_text(
        color = "grey50",
        size = 8,
        hjust = c(0)
      ),
      plot.caption.position = "panel",
      axis.title.x = element_text(angle = 0,
                                         color="grey50",
                                         hjust=1),
      axis.text.x = element_text(size = 9, 
                                 color = "grey50"),
      axis.title.y = element_blank(),
      axis.text.y = element_text(size = 9,
                                 color="grey50"),
      panel.grid.minor.x = element_blank(),
      panel.grid.major.x = element_blank(),
      panel.grid.minor.y = element_blank(),
      panel.spacing = unit(0.25, "cm"),
      panel.spacing.y = unit(0.25, "cm"),
      strip.text = element_text(
        angle = 0,
        size = 9,
        vjust = 1,
        face = "bold"
      ),
      legend.title = element_text(
        color = "grey30",
        face = "bold",
        vjust = 1,
        size = 7
      ),
      legend.text = element_text(
        size = 7,
        color = "grey30"
      ),
      legend.justification = "left",
      legend.box = "horizontal", # arrangement of multiple legends
      legend.direction = "vertical",
      legend.margin = margin(l = 0, t = 0, unit = "cm"),
      legend.spacing.y = unit(0.07, units = "cm"),
      legend.text.align = 0,
      legend.box.just = "top",
      legend.key.height = unit(0.2, "line"),
      legend.key.width = unit(0.5, "line"),
      text = element_text(size = 3)
    )
}

@@

![](attransperency_files/list_example - Copy.PNG){width="100%"}

@@

```{r code_folding="Code: Extract text from pdfs"}
my_path <- here::here("_blog_data", "MP_activities", "BezBegrBVGPar9-NR.pdf")

@@

```{r echo=FALSE, tidy=FALSE, R.options=list(width=10), code_folding=NULL}
stringr::str_wrap(df_all$text_raw[1], 10)
```

@@

```{r, code_folding=FALSE}
df_all <- df_all %>%
  mutate(name = str_extract(text_raw, regex("(?<=Einkommenskategorie)(?s).*(?=für das Jahr)", ignore_case = T)) %>%
    str_remove(., "\\(i\\)") %>%
    str_trim()) %>%
  mutate(income_category_19_raw = str_extract(text_raw, regex("(?<=2019:\\s?)\\S"))) %>% 
  mutate(income_category_19=case_when(income_category_19_raw=="-" ~ 0,
                                      TRUE ~ as.numeric(income_category_19_raw))) %>% 
    replace_na(., list(income_category_19="missing")) %>%
  select(-income_category_19_raw)

@@

```{r code_folding=FALSE}
df_income <- df_all %>%
  select(name, income_category_19) %>%
  distinct()

nrow(df_all)
nrow(df_income)
```

@@

```{r, code_folding="Code: Number of MPs per income bracket"}
tbl_income <- df_income %>% 
  count(income_category_19) %>% 
  gt() %>% 
  gt::cols_label(income_category_19=md("**income category**"),
                 n=md("**number of MPs**")) 
```

```{r echo=FALSE, code_folding=NULL}
tbl_income
```

@@

```{r, code_folding="Code: MPs with with missing income data"}
df_income_missing <- df_income %>% 
  filter(income_category_19=="missing") %>% 
  mutate(family_name=str_remove(name, ",.*$") %>% 
           str_extract(., "\\S*$"))

@@

```{r echo=FALSE, code_folding=NULL}
tbl_missing
```

@@

df_mp_dates <- readr::read_rds(file=here::here("_blog_data", "MP_activities", "MP_dates.rds"))
```

@@

#apply funciton to all links
df_mp_dates <- df %>%
  mutate(mp_dates=map(link, ~fn_get_dates(.)))

@@

```{r include=FALSE}
#extract family name for subsequent merger with income data
df_mp_dates <- df_mp_dates %>% 
  mutate(family_name=str_trim(title) %>% 
           str_extract(., regex("^\\S*")))

@@

```{r echo=FALSE, code_folding=NULL}
df_income_missing %>% 
  gt() %>% 
  gt::cols_label(mp_dates=md("**entry date**"),
                 name=md("**MP**"))
```

@@

```{r echo=TRUE, code_folding="Code: Remove MPs joining outside of reporting period"}
nrow(df_income)
df_income <- df_income %>% 
  filter(!name %in% df_income_missing$name)
nrow(df_income)
```

@@

```{r, code_folding=FALSE}
#get a clean name, without any academic or prefessional titles
df_income <- df_income %>% 
  mutate(name_family=str_remove(name, ",.*$") %>% 
           str_extract(., "\\S*$"),
         .after=name) %>% 
  mutate(name_clean=name %>% str_remove(., regex(",.*$")) %>% 
           str_remove_all(., regex("\\S*\\.")) %>% 
           str_remove_all(., regex("\\(.*\\)")) %>% 
           str_trim())

@@

```{r, code_folding=T}
df_gender <- df_income %>% 
  group_by(income_category_19, gender) %>% 
  summarise(n_obs=n()) %>% 
  mutate(n_rel_category=n_obs/sum(n_obs)) %>% 
  group_by(gender) %>% 
  mutate(n_gender=sum(n_obs)) %>% 
  ungroup() %>% 
  mutate(n_rel_gender=n_obs/n_gender)

pl_gender_category <- df_gender %>% 
  # filter(gender=="female") %>% 
  mutate(gender=fct_rev(gender)) %>% 
  ggplot()+
  labs(title=glue("Austrian Nationalrat: Share of <span style  = color:{gender_colors['female']}>female</span> and <span style = color:{gender_colors['male']}>male</span> MPs per income category"),
       subtitle=str_wrap("Income: average monthly income from professional positions in addition to MPs' salary. Absolute number of female MPs in brackets. Only lower chamber. Data for 2019.", 105),
       y="[income category] average monthly income",
       caption=my_caption)+
  geom_bar(aes(y=income_category_19,
               x=n_obs,
               fill=gender),
           stat="identity",
           position="fill")+
  geom_text(data=. %>% filter(gender=="female"),
            aes(y=income_category_19,
                x=n_rel_category-0.01,
                label=paste0(round(n_rel_category,2) %>% 
                  percent(scale=100),
                  "\n(",
                  n_obs,
                  ")")),
            color="white",
            lineheight=0.6,
            hjust=1,
            stat="identity")+
  geom_vline(xintercept = .5,
             color="white",
             linetype="dashed"
             )+
  scale_fill_manual(values=gender_colors)+
  scale_x_continuous(label=scales::label_percent(),
                     expand=expansion(mult=c(0, 0.05)))+
  scale_y_discrete(labels=income_categories_short,
                   expand=expansion(mult=c(0, 0)),
                   position = "left")+
  theme_post()+
  theme(legend.position="none",
        plot.title=element_markdown(),
        axis.title.x=element_blank(),
        axis.title.y.left = element_text(angle = 90,
                                         color="grey50",
                                         hjust=1),
        axis.text.y.left = element_text(),
        axis.text.y.right = element_blank(),
        axis.title.y.right = element_blank(),
        panel.grid.major.y  = element_blank())

@@

```{r echo=FALSE, fig.height=6, fig.width=10, code_folding=NULL}
pl_gender_category

@@

```{r, code_folding=F}
pl_gender_intra_dist <- df_gender %>% 
  ggplot()+
  labs(title="Austrian Nationalrat: Distribution of MPs over income groups per gender",
       subtitle=str_wrap("Income: average monthly income from professional positions in addition to MPs' salary. Absolute number of MPs in brackets. Only lower chamber. Data for 2019.", 105),
       x="[income category] average monthly income",
       caption=my_caption)+
  geom_bar(aes(x=income_category_19,
               y=n_rel_gender,
               fill=gender),
           stat="identity")+
  geom_text(aes(x=income_category_19,
                y=n_rel_gender+0.02,
                label=paste0(percent(n_rel_gender, accuracy = 0.1),
                             "\n",
                             "(", n_obs, ")")),
            lineheight=0.7,
            stat="identity")+
  scale_fill_manual(values=gender_colors, 
                    na.value = "grey30")+
  scale_x_discrete(labels=income_categories_short)+
  scale_y_continuous(label=scales::label_percent(accuracy=1),
                     expand=expansion(mult=c(0, 0.1)))+
  facet_wrap(vars(gender))+
  theme_post()+
  theme(legend.position = "none",
        axis.title.x = element_text(angle = 0,
                                         color="grey50",
                                         hjust=1),)
```

@@

```{r echo=FALSE, code_folding=NULL}
pl_gender_intra_dist
```

# Party affiliation
## Get MPs' party membership

@@

```{r, code_folding="Code: Get party affiliation"}
wiki_link <- "https://de.wikipedia.org/wiki/Liste_der_Abgeordneten_zum_%C3%96sterreichischen_Nationalrat_(XXVII._Gesetzgebungsperiode)"

@@

```{r echo=FALSE, code_folding=F}
datatable(df_income %>% select(name, party, gender, income_category_19),
          colnames=c("MP name"="name", "income category"="income_category_19"),
          filter="top",
          options=list(pageLength=10,
                       columnDefs = list(list(className = 'dt-center', targets = 1:3,
                                         searchable=TRUE))),
          rownames = FALSE)
```

@@

```{r, code_folding="Code: plots on income categories"}
df_agg <- df_income %>% 
  ungroup() %>%
  mutate(income_category_19_fac=as_factor(income_category_19) %>% 
           fct_inseq()) %>% 
  mutate(party=fct_infreq(party)) %>% 
  group_by(income_category_19, party, .drop = F) %>% 
  summarise(n_obs=n()) %>% 
  group_by(party) %>% 
  mutate(n_obs_total=sum(n_obs)) %>% 
  mutate(n_obs_rel=n_obs/n_obs_total)

pl_rel <- df_agg %>% 
  ggplot()+
  labs(title="Austrian Nationalrat: Relative number of MPs per income category and party",
    subtitle=str_wrap("Percentages are shares of each party's total number of members. Absolute numbers in brackets. Lower chamber only (Nationalrat). Data for 2019.", 105),
    x="[income category] average monthly income",
    caption=my_caption)+
  geom_label(data=. %>% filter(n_obs_rel >0),
            aes(x=party,
                y=n_obs_rel+.3,
                family="Roboto Condensed",
                group=party,
                label=paste0(scales::percent(n_obs_rel,
                                      accuracy=0.1),
                            "\n",
                            "(", n_obs, ")")
                ),
            fill=plot_bg_color,
            label.size=0,
            label.padding = unit(0.1, "lines"),
            lineheight=0.7,
            family="Roboto Condensed",
            position=position_dodge2(width = 1))+
    geom_bar(aes(x=party,
               y=n_obs_rel,
               group=income_category_19,
               fill=party),
           position=position_dodge2(),
           stat="identity"
           )+
  scale_fill_manual(values=party_colors)+
  scale_x_discrete(labels=abbreviate)+
  scale_y_continuous(label=scales::label_percent(),
                     # limits = c(0, 1.15),
                     expand=expansion(mult=c(0, 0.15)))+
  lemon::facet_rep_wrap(vars(income_category_19),                        labeller=labeller(income_category_19=map_chr(income_categories_short, ~str_remove_all(., regex("\\]|\\["))) %>% 
                                                                                             map_chr(., ~str_replace(., regex("\\\n"), ": ")) %>%
                                                                                             map_chr(., ~paste0("Income category ", .))),
                        ncol=2,
                        repeat.tick.labels = TRUE)+
  theme_post()+
  theme(legend.position="none",
        axis.title.x = element_blank())
```

```{r echo=FALSE, code_folding=NULL}
pl_rel
```

@@

```{r echo=FALSE, code_folding=NULL}
pdf_file <- pdftools::pdf_data(pdf = my_path) 
datatable(pdf_file[[8]],
          options=list(pageLength=10,
                       columnDefs = list(list(className = 'dt-center', targets = 0:4)),
                       list(className='dt_left', targets=5)),
          rownames=FALSE)
```

@@

```{r, code_folding="Code: identifying new positions"}
df_linebreaks <- pdf_file[[8]] %>%
  select(y, text) %>% 
    arrange(y) %>%
    mutate(line_diff = y - dplyr::lag(y, default = 0)) %>%
    mutate(row_jump = case_when(
      line_diff > 11 ~ 1,
      TRUE ~ 0
    )) %>%
    mutate(row_indicator = cumsum(row_jump)) 
```

```{r echo=FALSE, code_folding=NULL}
datatable(df_linebreaks,
          options=list(pageLength=10,
                       columnDefs = list(list(className = 'dt-center', targets = "all"))),
          rownames=FALSE)
```

@@

```{r paged.print=TRUE, code_folding="Code: Table with one row per position"}
df_rows <- df_linebreaks %>% 
  group_by(row_indicator) %>%
    summarise(text_combined = paste(text, collapse = " ")) %>%
    mutate(text_combined = text_combined %>% str_trim() %>% str_squish())
```

```{r, ech=F, code_folding=NULL}
df_rows
```

@@

```{r, code_folding="Code: row numbers of sub-headings"}
# headings
heading_executive <- df_rows %>%
    filter(str_detect(text_combined, regex("Leitende Stellung in", ignore_case = T))) %>%
    pull(row_indicator)

@@

```{r, code_folding="Code: Function to extract positions"}
fn_get_positions <- function(x) {
  d <- x %>%
    arrange(y) %>%
    mutate(line_diff = y - dplyr::lag(y, default = 0)) %>%
    mutate(row_jump = case_when(
      line_diff > 11 ~ 1,
      TRUE ~ 0
    )) %>%
    mutate(row_indicator = cumsum(row_jump)) %>%
    group_by(row_indicator) %>%
    summarise(text_combined = paste(text, collapse = " ")) %>%
    mutate(text_combined = text_combined %>% str_trim() %>% str_squish())

@@

```{r, code_folding="Code: Apply function"}
df_data <- pdf_file %>%
  map_dfr(., fn_get_positions)

@@

```{r echo=FALSE, code_folding=NULL}
datatable(df_count,
          colnames=c("MP name"="name",
                     "# executive pos (total)"="executive_n",
                     "# executive pos not remunerated"="executive_non_remunerated_n",
                     "# other pos"="other_n",
                     "# honorary pos"="honorary_n",
                     "total # pos" = "total_n"),
          options=list(pageLength=10,
                       columnDefs = list(list(className = 'dt-center', targets = "all"))),
          rownames=FALSE)
```

@@

```{r, code_folding="Code: Number of paid positions and income category"}
df_income_positions <- df_count2 %>% 
  left_join(., df_income %>% select(gender, income_category_19, name),
            by="name") %>% 
  select(name_clean, name, contains("executive"), contains("other"), party, income_category_19) %>% 
  mutate(positions_paid=(executive_n-executive_non_remunerated_n)+other_n)

@@

```{r echo=FALSE, fig.height=15, code_folding=NULL}
girafe(ggobj = pl_income_positions)

@@

```{r, code_folding="Code: MPs with no income but paid positions"}
df_mp5 <- df_income_positions %>% 
  filter(income_category_19==0) %>% 
  filter(positions_paid>0) %>% 
  select(contains("name"), party, executive_n, positions_paid) %>% 
  left_join(., df_positions %>% select(name, executive_positions, other_positions), by=c("name"="name")) %>% 
  pivot_longer(cols=c(contains("positions"), -positions_paid),
               names_to="positions",
               values_to="positions_name") %>% 
  mutate(positions_chr=map(positions_name, deframe) %>% 
           map_chr(., ~paste(., collapse=";\n "))) %>% 
  select(-positions_name) %>% 
  pivot_wider(id_cols=c(name, party),
              names_from=positions,
              values_from=positions_chr)

@@

```{r, code_folding=">Code: MP share w at least one add. position"}
df_bar_position <- df_position_long %>% 
  filter(!position %in% c("executive_non_remunerated_n",
                        "total_n")) %>% 
  group_by(party, position) %>% 
  summarize(n_zero=length(number[number==0]),
            n_non_zero=length(number[number!=0])) %>% 
  ungroup() %>% 
  mutate(perc=n_non_zero/(n_non_zero+n_zero)) %>% 
  mutate(position=fct_relevel(position, "honorary_n", after = 2))

@@

```{r, code_folding="Code: different types of executive positions"}
df_executive <- df_count2 %>% 
    select(party, contains("executive")) %>% 
    mutate(executive_remunerated_n=executive_n-executive_non_remunerated_n) %>% 
  group_by(party) %>% 
  summarize(executive_no=length(executive_n[executive_n==0]),
    remunerated_yes=length(executive_remunerated_n[executive_remunerated_n>0]),
    remunerated_no=length(executive_remunerated_n[executive_remunerated_n==0 &
                            executive_n>0])) %>% 
  ungroup() %>% 
  rowwise() %>% 
  mutate(total=sum(c_across(where(is.numeric)), na.rm=T))
